The Astropy Project: Building an inclusive, open science project and status of the v2.0 software

### 2018-01-05 main.tex
try to clarify and specify what 'lazy loading' means in terms of FITS files.  I wasn't 100% sure here whether this is referring specifically to lazy loading of all HDUs or lazy loading of all data *in* HDUs - if someone can clarify this further, it would be helpful.

FITS files are now loaded \emph{lazily} (this default behavior can be
deactivated, if needed), where all HDUs are not loaded until
requested. This should provide substantial speed-ups when using the
convenience functions (e.g., \texttt{getheader()} or \texttt{getdata()}) to
get an HDU that is near the beginning in a file with many HDUs.

>>>>

FITS files are now loaded \emph{lazily} by default, i.e., an object
representing the list of HDUs is created but the data are not loaded into
memory until requested.  This approach should provide substantial speed-ups
when using the convenience functions (e.g., \texttt{getheader()} or
\texttt{getdata()}) to get an HDU that is near the beginning in a file with
many HDUs.
